Papers

### 2023-11-29 quarto/index.qmd
update

---
about:
  id: az-heading
  template: trestles
  image: img/aston.jpg
  image-width: 200px
  image-shape: rounded
  links:
    - icon: twitter
      text: Twitter
      href: https://twitter.com/astonzhangAZ
    - icon: github
      text: GitHub
      href: https://github.com/astonzhang
---

@@

>>>>

---
about:
  id: az-heading
  template: trestles
  image: img/aston.jpg
  image-width: 200px
  image-shape: rounded
  links:
    - icon: twitter
      href: https://twitter.com/astonzhangAZ
    - icon: bi-envelope
      href: img/email.png
    - icon: github
      href: https://github.com/astonzhang
    - icon: google
      href: https://scholar.google.com/citations?user=WXOaxKMAAAAJ
---

@@

*<FONT COLOR="#ff0000">I'm hiring</FONT> one Ph.D. research intern at the large language model (Llama) team of Meta GenAI. If you are interested in LLM pre-training and fine-tuning research in 2024, just <a href="img/email.png" target="_blank">email me</a>.*
